Demystifying the Computer Science PhD Admission in the US\\{\large A Guide for International Students

### 2023-11-24 demystify.tex
updates

The primary focus of the admissions committee is to \textbf{evaluate your background and interest in research} since a PhD in Computer Science and determine if you would \textbf{fit into} the program. To evaluate your profile, we consider
the following key indicators, listed in order of importance.

@@

Many students have letters written by themselves and signed by their professors. These have little
values. We can recognize them and will consider them weakness.
Also, many professors write generic letters for students, e.g., the students didn't do any
research or make any impression for the professor to write about. These letters are also not useful and considered weak.  It might be a good idea to directly ask if the prof. is willing to write a \emph{strong} letter for you. If not, then you should ask someone else.  For example, if a student I don't know well ask me to write letter for them, I will explicitly tell them I don't know them that well to write about them in details, and such a short, generic, and weak letter will hurt their chance.

@@

Reviewers might raise concerns (a red flag) about  a letter that is not waived, e.g., they will think that if you do not trust your letter writers, then you should find someone else to write for you. In short, it's a standard practice and a way of keeping things straightforward and respectful in the whole recommendation game.

>>>>

The primary focus of the admissions committee is to \textbf{evaluate your background and interest in research} (a PhD in Computer Science is a research degree!), and determine if you would \textbf{fit into} the program. To evaluate your profile, we consider
the following key indicators, listed in order of importance.

@@

Many students have letters written by themselves and signed by their professors. These have little
values. We can recognize them and will consider them weakness.
Also, many professors write generic letters for students, e.g., the students didn't do any
research or make any impression for the professor to write about. These letters are also not useful and considered weak.  It might be a good idea to directly ask if the prof. is willing to write a \emph{strong} letter for you. If not, then you should ask someone else.  For example, if a student I don't know well ask me to write letter for them, I will explicitly tell them I don't know them that well to write much about them, and such a short, generic, and weak letter will not help their profile.

@@

Reviewers might raise concerns (a red flag) about  a letter that is not waived, e.g., if you do not trust your letter writers, then you should find someone else to write for you. In short, it's a standard practice and a way of keeping things straightforward and respectful in the whole recommendation game.
